Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping

### 2018-04-29 stp/paper/main.tex

To evaluate our new system \serene{}\footnote{ \url{http://github.com/NICTA/serene-python-client/tree/stp/stp}}, we show that its semantic labeling model 
produces more accurate matches for attributes and that the CP formulation leads 
to better semantic models in terms of precision and recall.

>>>>

To evaluate our new system \serene{}\footnote{ http://github.com/NICTA/serene-python-client/tree/stp/stp}, we show that its semantic labeling model 
produces more accurate matches for attributes and that the CP formulation leads 
to better semantic models in terms of precision and recall.
